---
title: "STAT 506 <br> Advanced Regression Analysis"
output:
  revealjs::revealjs_presentation:
    theme: white
    center: true
    transition: none
    incremental: true
---
```{r setup, include=FALSE}
require(ggplot2)
```

## Tidyverse Demo

>- The `tidyverse` contains `dplyr`, `ggplot2` and a set of other useful R packages. 
 
>- Most of the packages in the tidyverse were created by Hadley Wickham.

>- The tidyverse is a modern way to express R code for data wrangling, storage, and visualization.

```{r, eval = F}
install.packages('tidyverse')
```

## Loading Packages
There are two steps for using packages: installation and loading.

```{r}
library(tidyverse)
```

## Reading Data into R

>- The [readr](https://readr.tidyverse.org) package is very useful for reading data into R.


```{r}
okcupid <- read_csv('http://math.montana.edu/ahoegh/teaching/stat408/datasets/OKCupid_profiles_clean.csv')
```


## Data Manipulation with dplyr

>- [dplyr](https://dplyr.tidyverse.org) is useful for data manipulation and can be characterized by a set of verbs:
  >- select
  >- filter
  >- group_by
  >- mutate
  >- sample...


```{r}
sample_n(okcupid,2)
```


## piping with %>%

>- The symbol %>% is a piping operator that can be used to connect commands

```{r}
okcupid %>% group_by(sex) %>% summarize(average_age = mean(age))
```


## Graphics with ggplot2

>- [ggplot](https://ggplot2.tidyverse.org) stands for the grammar of graphics and can be used to create figures in R.

>- Layers of ggplot components are layered on top of each other using the + operator.

```{r, eval = F}
okcupid %>% filter(sex == 'm') %>% 
  ggplot(aes(x = body_type, y = height)) + 
  geom_violin() + 
  ggtitle("Male Heights by Self-Reported Body Type") + 
  xlab('Self Reported Body Type') + 
  ylab('Height (inches)') +
  geom_jitter(alpha = .01)
```


## Homework 1

>- Homework 1 is posted on the course webpage and will be due Monday January 20 at 10 AM.


## Graphics with ggplot2

```{r, echo = F}
okcupid %>% filter(sex == 'm') %>% ggplot(aes(x = body_type, y = height)) + geom_violin() + ggtitle("Male Heights by Self-Reported Body Type") + xlab('Self Reported Body Type') + ylab('Height (inches)') + geom_jitter(alpha = .01)
```
